Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-16 Docs/IJES/journal.tex
revised version of the paper

@@

@@

We presented five approaches to solve the HW-SW partitioning problem and compared them to other state-of-the-art techniques. Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP. Below that, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and notorious. ESBMC-PB is a viable alternative for a number of nodes lower than $150$. GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.

If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler. However, ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free. Experimental results also pointed to an improvement of ESBMC, when using a parallel approach. In particular, all three parallel approaches described in this paper produced expressive results. The fastest ESBMC approaches is ESBMC-PB, which produces good results for an intermediate amount of edges and nodes. Thus, considering that nowadays processors have more and more cores, when modeling the problem, it is possible to consider multi-core model checking as an alternative to solve the HW-SW partitioning problem.

>>>>

\textcolor{blue}{We have to point out that the experimental results presented here depend on the computer’s processor and memory, the version of each tool (MATLAB and ESBMC), and the partitioning problem to be solved. Additionally, any change from MATLAB to another tool or to GA/ILP libraries for different programming languages can influence the measured time of the algorithms.}

@@

\textcolor{blue}{Regarding the amount of MO of sequential ESBMC, it has to explore all the states until to find out the answer of HW-SW partitioning, and it starts from an extreme where all the variables are selected as software, and go testing incrementally one by one. In the other hand, all the multi-core ESBMCs and SBMC-$\nu$Z, are optimized to reach faster the result, without the need to explore the states as sequential ESBMC does. Therefore, when the partitioning problem grows in complexity is natural do reach MO with sequential ESBMC.}

@@

We presented five approaches to solve the HW-SW partitioning problem and compared them to other state-of-the-art techniques. Experimental results showed that for a number of nodes larger than $300$, the best solution for the HW-SW partitioning problem is ILP. \textcolor{blue}{Below that limit of nodes, the best solution turns out to be ESBMC-$\nu$Z since its execution time is faster and its result precise.} ESBMC-PB is a viable alternative for a number of nodes lower than $150$. GA had an intermediate result in terms of performance, but the error presented from exact solution made it not acceptable to that kind of application.

If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler. \textcolor{blue}{However, ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free. However, it is possible to use free GA and ILP libraries (BSD-Style and MIT licenses) as well.}

Experimental results also pointed to an improvement of ESBMC, when using a parallel approach. The fastest ESBMC approach is ESBMC-PB, which produces good results for an intermediate amount of edges and nodes. Thus, considering that nowadays processors have more and more cores, when modeling the problem, it is possible to consider multi-core model checking as an alternative to solve the HW-SW partitioning problem.
